\section{Conclusion}
Throughout my internship at Statcon Electronics India Ltd., I gained extensive
knowledge and practical experience in implementing Space Vector Pulse Width
Modulation (SVPWM). This journey involved understanding and applying various
mathematical transformations, developing control algorithms, and transitioning
from simulation to real hardware implementation.

\noindent
SVPWM offers several advantages over conventional techniques, such as:
\begin{itemize}
    \item \textbf{Higher Efficiency}:SVPWM maximizes the DC bus voltage utilization, leading to improved efficiency in inverter operation.
    \item \textbf{Reduced Harmonic Distortion}:By optimizing the switching sequences, SVPWM reduces the harmonic distortion in the output waveforms.
    \item \textbf{Improved Power Factor}:SVPWM enables better control over the output voltage and current, contributing to an improved power factor.
\end{itemize}

\section{Future Scope}
The knowledge and skills developed during this internship have broad
applications in various fields, including:

\begin{itemize}
    \item \textbf{Hybrid Inverters}:Enhancing the efficiency and performance of hybrid inverters.
    \item \textbf{Active Front Ends}: Driving DC series motors in trains for power factor correction and voltage regulation.
    \item \textbf{Battery Charging}: Implementing SVPWM for efficient battery charging systems.
\end{itemize}

Overall, this internship has been a valuable learning experience, providing me
with the technical expertise and practical skills needed to contribute
effectively to the field of power electronics and embedded systems.